External Patch Group Prior Guided Adaptive Orthogonal Dictionary Learning for Real Image Denoising

### 2016-10-22 CVPR2017_Review_Unified.tex
add

%%%%%%%%% TITLE
\title{External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising}

@@

\subsection{External Prior Guided Internal Subspace Learning}
Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering. The mean substracted PG is defined as $\mathbf{\overline{Y}}$. To project this PG into a most adaptive subspace, we select the most suitable Gaussian component to it from the PG-GMM trained in previous section. The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
\begin{equation}\label{equ3}
P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})}.
\end{equation}
Since the noise on real images are mostly small when compared to the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$. Finally, the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ is selected as the most suitable subspace for $\mathbf{\overline{Y}}$.

Though each PG has been projected into its most suitable subspace, the pre-learned subspace is still too general to represent the noisy PG extracted from the real noisy image. That is, the noisy PGs projected into one cluster can still constisted a subspace which is of lower dimensions than the subspace pre-learned from the external PGs. This can be demonstrated by compare the distribution of external PGs and internal PGs in the same clusters. We randomly select one cluster, and collect the celan PGs extracted from external dataset (Kodak 24 images) and the niosy PGs from the testing image. Since the original PGs are of $3p^{2}$ dimensions, we apply PCA to project the PGs into 2 dimensions for better visualization. The results is shown in Figure \ref{fig}, from which we can see clearly that the projected PGs are mainly in a smaller region of the external PGs, which proves that the internal PGs are only consisted a subspace in a lower dimension than the PGs collected from external subspace. To better and adaptively charactering the internal PGs from the testing image, we need learn a more specific dictionary for noisy PGs assigned into each cluster. For notation simplicity, we ignore the index of subspace $k$. The internal PGs $\mathbf{Y}$ form a subspace which can be obtained by singular value decomposition (SVD),
\begin{equation}\label{equ4}
\mathbf{Y}=\mathbf{U}\mathbf{S}\mathbf{V}^{T}
\end{equation}
The singular vectors capture the statistical structures of NSS variations in natural images, while the singular values in $\mathbf{S}$ represent the significance of these singular vectors. Fig.\ 4 shows the singular vectors for one Gaussian component.

>>>>

%%%%%%%%% TITLE
\title{External Patch Group Prior Guided Adaptive Orthogonal Dictionary Learning for Real Image Denoising}

@@

\subsection{External Prior Guided Adaptive Orthogonal Dictionary Learning}
Given a rael noisy image, we extract noisy PGs from it and save the mean vectors of each PG for recovering. The mean substracted PG is defined as $\mathbf{\overline{Y}}$. To project this PG into a most adaptive subspace, we select the most suitable Gaussian component to it from the PG-GMM trained in previous section. The selection can be done by checking the posterior probability that $\mathbf{\overline{Y}}$ belongs to the $k$th Gaussian component:
\begin{equation}\label{equ3}
P(k|\mathbf{\overline{Y}})=\frac{\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{k})}{\sum_{l=1}^{K}\prod_{m=1}^{M}\mathcal{N}(\mathbf{\overline{y}}_{m}|\mathbf{0},\mathbf{\Sigma}_{l})}.
\end{equation}
Since the noise on real images are mostly small when compared to the signals, the covariance matrix of the $k$th component is still $\mathbf{\Sigma}_{k}$. Finally, the component with the maximum A-posteriori (MAP) probability $\ln P(k|\mathbf{\overline{Y}})$ is selected as the most suitable subspace for $\mathbf{\overline{Y}}$.

Though each PG has been projected into its most suitable subspace, the pre-learned subspace is still too general to represent the noisy PG extracted from the real noisy image. That is, the noisy PGs projected into one cluster can still constisted a subspace which is of lower dimensions than the subspace pre-learned from the external PGs. This can be demonstrated by compare the distribution of external PGs and internal PGs in the same clusters. We randomly select one cluster, and collect the celan PGs extracted from external dataset (Kodak 24 images) and the niosy PGs from the testing image. Since the original PGs are of $3p^{2}$ dimensions, we apply PCA to project the PGs into 2 dimensions for better visualization. The results is shown in Figure \ref{fig}, from which we can see clearly that the projected PGs are mainly in a smaller region of the external PGs, which proves that the internal PGs are only consisted a subspace in a lower dimension than the PGs collected from external subspace. To better and adaptively charactering the internal PGs from the testing image, we need learn a more specific dictionary for noisy PGs assigned into each cluster. For notation simplicity, we ignore the index of subspace $k$. The internal PGs $\mathbf{Y}$ form a subspace which can be obtained by singular value decomposition (SVD),
\begin{equation}\label{equ4}
\begin{split}
&\min_{\mathbf{D}\in \mathbb{R}^{3p^2\times r}}\|\mathbf{Y}-[\mathbf{D}_{e};\mathbf{D}_{i}]\mathbf{A}\|_{F}^{2}+\lambda\|\mathbf{A}\|_{1}
\\
&
\text{s.t.}
\quad
\mathbf{D}_{i}^{T}\mathbf{D}_{i} = \mathbf{I}_{r},\ \mathbf{D}_{e}^{T}\mathbf{D}_{i} = \mathbf{0},
\end{split}
\end{equation}
The singular vectors capture the statistical structures of NSS variations in natural images, while the singular values in $\mathbf{S}$ represent the significance of these singular vectors. Fig.\ 4 shows the singular vectors for one Gaussian component.
